Effects of pre-existing structures on the seismicity of the Charlevoix Seismic Zone

### 2019-07-01 main_full_manuscript.tex
Minor changes

%%%%%%%%%%%%%%
\acknowledgments
This project is supported by the National Science Foundation (NSF - ICER) under the award title ``EarthCube Building Blocks: Collaborative Proposal: GeoTrust: Improving Sharing and Reproducibility of Geoscience Applications'' with an award number 1639706. We acknowledge the high performance computing (HPC) resource center at the University of Memphis, TN for providing the computing time for this research. Earthquake dataset are available from Earthquakes Canada, GSC, Earthquake Search (On-line Bulletin), http://earthquakescanada.nrcan.gc.ca/stndon/NEDB-BNDS/bulleng.php, Natural Resources Canada (1/30/2019).

>>>>

%%%%%%%%%%%%%%
\acknowledgments
This project is supported by the National Science Foundation (NSF - ICER) under the award title ``EarthCube Building Blocks: Collaborative Proposal: GeoTrust: Improving Sharing and Reproducibility of Geoscience Applications'' with an award number 1639706. We acknowledge the high performance computing (HPC) resource center at the University of Memphis, TN for providing the computing time for this research. Earthquake dataset are available from Earthquakes Canada, GSC, Earthquake Search (On-line Bulletin), http://earthquakes canada.nrcan.gc.ca/stndon/NEDB-BNDS/bulleng.php, Natural Resources Canada (1/30/2019).
